WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-22 article/Article.tex
give url to download the rpm packages
darcs-hash:20060322120431-2fc9d-3030ebcad1bcf475e067a7389db25364eabe8405.gz
comment are remove TODO items
darcs-hash:20060322120514-2fc9d-96e9321d8e9e9ebc8e54a8e461441b48796a915a.gz
talk about contributing
darcs-hash:20060322120555-2fc9d-9e22fee82f128c8e558660ec2c2a3aab7d019fcf.gz

A rpm package for Mandriva Linux will be available soon.

TODO: provide more binary packages - for mac and windows.

@@

TODO: rename ItkVtk to ItkVtkGlue to avoid problems wiht non-case sensitive filesystems.

@@

- test
- Work on tcl, java, and others
- add more classes

talk about darcs

>>>>

RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.

% TODO: provide more binary packages - for mac and windows.

@@

@@

WrapITK is an opensource project, and so all contributions are welcome. Here are
some points which requires special attention:
\begin{itemize}
  \item Test it and report problem. That's the more important thing to do:
we need feedbacks to enhance WrapITK quality !
  \item Work on tcl, java, and others. We are not tcl or java developers, and so
are not able to complete the work for those languages. Any help from tcl and
java expert would be highly appreciated. Also, there is no reason to be limited
to python, tcl and java, and WrapITK can be extended to other languages supported
by swig like perl, ruby, ocaml and others.
  \item Add more classes. WrapITK add lots of new classes compared to the current
wrapping system, but there is still lots of work to do, especially to support more
filter dedicated to \verb$Vector$ pixels.
\end{itemize}

\verb$darcs$ allow to easily contribute to WrapITK, by sending patch by email with
the command \verb$darcs send$, while keeping credits for the work done.
Feel free to send patches; they will be tested and integrated in the project.

A web interface (\url{http://auriga.wearlab.de/~alb/darcsweb/}) for the WrapITK darcs
repository is available at \url{http://voxel.jouy.inra.fr/darcsweb/}.
